---
title: "Water Sr:Ca & Otolith Sr Data Analysis"
output:
  word_document: default
  html_document:
    highlight: tango
    theme: united
---

## Water Chemistry

### Water Sr:Ca between two rivers across 7 yrs
```{r, echo=FALSE, warning=FALSE}
dfn_water <- read.csv("Data/water_summarySE.csv", header = T)
dfn_water$year <- factor(dfn_water$year)

library(ggplot2)
ggplot(dfn_water, aes(x=year, y=Sr.Ca, fill=site, width=0.85))+
  geom_bar(stat="identity", position="dodge", colour="black")+
  geom_errorbar(aes(ymin=Sr.Ca-sd, ymax=Sr.Ca+sd),width=.3, position=position_dodge(0.9))+
  xlab("Year")+ylab("Mean water Sr:Ca (ppb:ppm) ± SD")+
  scale_fill_manual(values = c("white","grey"))+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor=element_blank(),
        axis.title.x=element_text(size=16, colour = "black", margin = unit(c(5, 0, 0, 0), "mm")),
        axis.title.y=element_text(size=16, colour = "black", margin = unit(c(0, 5, 0, 0), "mm")),
        axis.text=element_text(size=14, colour = "black"),legend.title=element_blank(), legend.position="none" )+
  annotate("text", x=4:7-0.2, y=c(14,12,15,15), label=c("a","a","a","a"), size=6)+
  annotate("text", x=4:7+0.2, y=c(26,22,35,31), label=c("bc","c","b","bc"), size=6)

```

- white: Maumee River, gray: Sandusky River

### ANOVA of water Sr:Ca ~ year*site (2001, 2011, 2012, and 2013 data)

```{r, echo=FALSE}
## Read data
df_water <- read.csv("Data/water Sr Ca data.csv", header = T)
df_water <- df_water[,c("year","site","Ca..ppm.","Sr..ppb.","Sr.Ca")]
df_water1 <- subset(df_water, site=="Maumee River")
df_water2 <- subset(df_water, site=="Sandusky River")
df_water3 <- rbind(df_water1, df_water2)
df_water3$site <- factor(df_water3$site)
df_water3$year <- factor(df_water3$year)
df_water4 <- subset(df_water3, year=="2001"|year=="2011"|year=="2012"|year=="2013")
df_water4$year <- factor(df_water4$year)
anova_w <- aov(Sr.Ca ~ year*site, data=df_water4)
summary(anova_w)
```

### Tukey HSD (water Sr:Ca ~ year*site)

```{r, echo=FALSE }
TukeyHSD(anova_w)
```

## Otolith Sr

### Data summary
```{r, echo=FALSE}
#Read data and extract variables for analysis
df_oto <- df_oto <- read.csv("Data/larval oto chem age.csv", header = T)
df_oto1 <- df_oto[,c("year","location","otoSr.ppm")]
#convert year to categorical variable
df_oto1$year <- as.factor(df_oto1$year)
summary(df_oto1)

```

### ANOVA of oto Sr ~ year*location(site)

```{r, echo=FALSE}
#Test effects of Location (two rivers), Year, and Location*Year interaction on Otolith Sr 
anova1 <- aov(otoSr.ppm ~ location*year, data=df_oto1)
summary(anova1)

```

### Tukey HSD test (oto Sr ~ year*site)

```{r, echo=FALSE }
#TukeyHSD test
TukeyHSD(anova1)
```

### Basic Boxplot (Oto Sr between two rivers across 7 yrs)
```{r, echo=FALSE, fig.align='center', fig.width=9, fig.asp=0.7}
boxplot(otoSr.ppm ~ year, data=df_oto1, boxfill=rgb(1, 1, 1, alpha=1), border=rgb(1, 1, 1, alpha=1), xlab="Year",ylab="Otolith [Sr](ppm)", cex.lab=1.3)
boxplot(otoSr.ppm ~ year, data=df_oto1[which(df_oto1$location=="Maumee"),], xaxt = "n", add = TRUE, boxfill="white",boxwex=0.3, at=1:7 - 0.15)
boxplot(otoSr.ppm ~ year, data=df_oto1[which(df_oto1$location=="Sandusky"),], xaxt = "n", add = TRUE, boxfill="grey",boxwex=0.3, at=1:7 + 0.15)

```

### ggplot2 Boxplot (Oto Sr between two rivers across 7 yrs)

```{r, echo=FALSE, fig.align='center', fig.width=9, fig.asp=0.7}
library(ggplot2)

ggplot(data=df_oto1, aes(x=year, y=otoSr.ppm, fill=location))+
  geom_boxplot()+
  scale_fill_manual(values = c("white","grey"))+
  xlab("Year")+ylab("Otolith [Sr](ppm)")+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor=element_blank(),
        axis.title.x=element_text(size=16, colour = "black", margin = unit(c(6, 0, 0, 0), "mm")),
        axis.title.y=element_text(size=16, colour = "black", margin = unit(c(0, 5, 0, 0), "mm")),
        axis.text=element_text(size=14, colour = "black"),
        legend.position="none")+
  annotate("text",x=1:7-0.2, y=c(1600,1200,1200,1600,1200,1500,1400), label=c("a","a","a","a","a","a","a"), size=6)+
  annotate("text",x=1:7+0.2, y=c(2000,3200,2400,3200,1500,2900,2800), label=c("b","bc","bd","cd","ae","cd","bce"), size=6)


```

### ANCOVA of oto Sr ~ age*location)
```{r, echo=FALSE}
df_oto2 <- df_oto[,c("year","location","otoSr.ppm","age.d")]
df_oto2$year <- as.factor(df_oto2$year)
# Drop data have no age 
df_oto2 <- na.omit(df_oto2)
# Drop unused factor (year 2001)
df_oto2$year <- factor(df_oto2$year);summary(df_oto2)

```

```{r,}
#ANOVA with interaction between age and river
mod1 <- aov(otoSr.ppm ~ age.d*location, data=df_oto2);summary(mod1)

#ANOVA without interaction between age and river
mod2 <- aov(otoSr.ppm ~ age.d + location, data=df_oto2);summary(mod2)

#ANOVA of two models
anova(mod1,mod2)
```

Note:

- Interaction between age and location is significant (F = 14.9, P < 0.001) 

- Intercepts between two rivers are also significantly different (F = 343.8, P < 0.001) 

### Two linear regressions
```{r, echo=FALSE, fig.align='center', fig.width=9, fig.asp=0.5}
library(ggplot2)

ggplot(df_oto2, aes(x=age.d, y=otoSr.ppm, group=location, colour=location, shape=year))+
  geom_point(size=2)+
  geom_smooth(method = lm, se=F, fullrange=T)+
  scale_colour_manual(values = c("dark grey","black"))+
  xlab("Age (d)")+ylab("Otolith [Sr](ppm)")+
  scale_y_continuous(breaks=seq(0, 2500, 500))+scale_x_continuous(breaks=seq(0, 24, 2))+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor=element_blank(),
        axis.title.x=element_text(size=16, colour = "black", margin = unit(c(5, 0, 0, 0), "mm")),
        axis.title.y=element_text(size=16, colour = "black", margin = unit(c(0, 5, 0, 0), "mm")),
        axis.text=element_text(size=14, colour = "black"),legend.title=element_blank() )
```

